Incentivizing Exploration with Unbiased History

### 2018-11-01 model.tex
Minor edit in the model.

\xhdr{Preliminaries.}
Throughout the paper, we will use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem. The former states that that a sum of independent random variables converges to its expectation quickly. The latter states that the CDF of an appropriately scaled average of IID random variables converges to the CDF of the standard normal distribution pointwise. In particular, the average strays far enough from its expectation with some guaranteed probability. The theorem statements are moved to Appendix~\ref{sec:prelim}.

>>>>

\xhdr{Preliminaries.}
\asedit{We assume that $K$ is constant, and focus on the dependence on $T$. However, we explicitly state the dependence on $K$, \eg using the $O_K()$ notation.}

Throughout the paper, we use the standard concentration and anti-concentration inequalities: respectively, Chernoff Bounds and Berry-Esseen Theorem. The former states that that a sum of independent random variables converges to its expectation quickly. The latter states that the CDF of an appropriately scaled average of IID random variables converges to the CDF of the standard normal distribution pointwise. In particular, the average strays far enough from its expectation with some guaranteed probability. The theorem statements are moved to Appendix~\ref{sec:prelim}.
